---
title: "Bayesian_tpc_fitting"
author: "Jason R Laurich"
date: "`r Sys.Date()`"
output: html_document
---

This file will upload data pertaining to Chlamydomonas growth rate (RFUs) over time, from 37 populations across a range of temperatures. We will use bayesTPC to fit thermal performance curves (TPCs) to this data and extract key curve parameters (Topt, Tmin, Tmax, Tbr, µmax) for each population.

------------------------------------------------------------------------------------------

Upload the packages

```{r packages}
library(tidyverse)
library(nimble) #required to run bayesTPC
library(bayesTPC)

```

Upload the data

```{r data}

data <- read.csv("data-processed/globe-chlamy-exponential-RFU-time.csv")
### setwd("data-processed") ### Have to run this in terminal for now, I cannot get the above command to work. I remember Amanda telling me something about tweaking the directory? Should be working though, getwd() tells me I'm in the right spot.

# For now, manually set the directory to data-processed
#again, for some reason I've got to input this manually!

# data<-read.csv("globe-chlamy-exponential-RFU-time.csv")

head(data)
str(data)
```

Clean the data

```{r data processing}
#Remove any missing data
data <- data %>% 
	dplyr::rename(temp = temperature) %>% 
	filter(!is.na(RFU)) 

#OK, let's create a matrix to hold the data for each population (1 to 15 here)
pops<-as.data.frame(1:15)
mat <- lapply(1:nrow(pops), function(z) data[which(data$population==pops[z,1]),])

#Check it
head(mat[[10]])
#Looks good!

```


Plot the data

```{r plot exploration}
#Let's look at the raw RFU data for a couple populations

#Joey's formulation
rfu %>% 
	filter(population == 15) %>% 
	ggplot(aes(x = days, y = RFU, color = factor(temp))) + geom_point()

#This works with the data in matrix form
ggplot(aes(x = days, y = RFU, colour = factor(temp)), data=mat[[3]]) + geom_point()
ggplot(aes(x = days, y = RFU, colour = factor(temp)), data=mat[[9]]) + geom_point()

#So does this
for (i in 1:2){
  print(ggplot(aes(x = days, y = RFU, colour = factor(temp)), data=mat[[i]]) + geom_point())
}

```

Fit the TPCs using bayesTPC

```{r}


```

